Title here

### 2017-01-13 portfolio/text/ms.Rmd
Format paper

<!-- Introduction, Methods, Results, Discussion, Conclusion -->
<!-- 600, 900, 500, 800, 200, -->

# Abstract

<!-- TODO < 250 words -->

Individuals relying on the extraction of natural resources for their livelihood
--- fishers, farmers, miners, and loggers, among others --- face high levels of
income variability driven by a mix of environmental, biological, management, and
economic dynamics. A key component to managing these industries is identifying
how regulatory actions and individual behaviour affect income variability and by
extension economic stability and the sustainable use of natural resources. For
commercial fisheries, communities and vessels fishing a greater diversity of
species have less revenue variability than those fishing a lower diversity.
However, it is unclear if these benefits extend to the actions of individual
fishers and how year-to-year changes in diversification affect revenue and
revenue variability. Here, we identify three axes by which fishers in Alaska,
one of the world's most productive fishing regions, can diversify fishing
activities. We show that, despite increasing specialization over the last 30
years, fishing permits with higher species diversity reduces individual revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of existing permits has a fishery-dependent effect on revenue and is
usually (`r g2_dens`% probability) associated with increased revenue uncertainty
the following year. Our results demonstrate that the most effective option for
individuals to decrease revenue variability is to purchase permits to
participate in additional or more diverse fisheries. However, this option is
expensive, often limited by regulations such as catch share programs, and
consequently unavailable to many individuals. With increasing environmental
variability in a changing climate, it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce income variability.

<!-- TODO: take home is the management context is key and controls show that
it's more complicated. TODO mentioned that specializing tends to be profitable
-->

\clearpage

@@

Managing natural resources and sustaining the livelihoods of those that depend
on their extraction is hard. These livelihoods tend to have high annual
variability in income relative to other professions [@mishra2002; @sethi2012b].
In addition to economic risk, such as changes in demand or prices, individuals
dependent on natural resources are also subject to biological and environmental
variability [@smith1986]. For example, drought and flooding are a major source
of risk for agricultural food security and farmers' incomes [@gregory2005], and
catastrophic disease outbreaks and wildfires increase risk for the logging
industry [@kirilenko2007].

@@

@@

Comparing single permit holders to individuals holding that same permit plus
additional permits illustrates the expected reduction in revenue variability
from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\ref{fig:spoke-all}). For example, individuals fishing a halibut permit plus
one additional permit always had lower expected revenue variability compared to
individuals fishing only a halibut permit (median reduction of `r
100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually increased expected revenue, although the permits
themselves represent a significant expense.

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given set of permits is more variable
(Fig. \ref{fig:within}). After accounting for fishing effort and changes in
annual average revenue for fishers with the same set of permits, specializing
tends to be associated with increased revenue but also increased variability
(Fig. \ref{fig:within}; Figs S\ref{fig:fe}, S\ref{fig:re}, S\ref{fig:noeffort}).
On average, there is a ~0.5% increase in the year-to-year revenue ratio per 1%
decrease in species diversity, and across strategies weighted equally, `r
g2_dens`% of the probability density supports a positive relationship between
specialization and revenue.

Changing (increasing or decreasing) an individual's fished species diversity
within the constraints of a set of permits tends to be associated with greater
expected variability or uncertainty in year-to-year revenue (Fig.
\ref{fig:within} strategies above zero; Figs. S\ref{fig:fe}, S\ref{fig:re},
S\ref{fig:mirror}). This effect was strongest for individuals with a halibut
permit or halibut and sablefish permits. Individuals with these strategies
experienced a ~2% increase in variability for a 1% change in the year-to-year
ratio of species diversity (Fig. \ref{fig:within}). Becoming more generalized in
species diversity also leads to increased revenue variability (Fig.
S\ref{fig:mirror}A), suggesting that the act of changing strategies is
a contributor to increased variability of revenue.

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994, which potentially confounds our estimates with
a major regulatory change. Therefore, we refit our models allowing all
strategy-level effects involving halibut and sablefish permits to vary
separately before and after the introduction of IFQs. The introduction of IFQs
reduced variability in revenue by ~25% (TODO XX--XX 95% CI) for individuals with
only halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

@@

There are many possible barriers to diversification for individuals relying on
natural resources for their livelihood. A primary barrier is the cost of
diversifying. For commercial fishers, purchasing additional licenses and gear
typically represents a substantial expense. Related barriers are apparent in
other natural resource sectors. For example, diversification has been positively
linked with total income or access to financial capital for farmers
[@abdulai2001; @barrett2001], small-scale fishing communities [@olale2012], and
those relying on forest resources [@illukpitiya2008]. Another major barrier to
diversification can be management restrictions. In commercial fisheries,
regulations that have been shown to reduce overfishing --- including improved
assessments [@melnychuk2017] and individual quota systems [@costello2008] ---
may ultimately restrict individual diversification [@smith1986; @kasperski2013]
or at least make developing a diverse fishing portfolio more expensive. However,
individual quota systems, in particular, may also reduce income variability
(Fig. S\ref{fig:ifq}A) perhaps offsetting the effects of reduced diversification
[@holland2016].

@@

\bibliographystyle{pnas2011}
\bibliography{refs}

\clearpage

# Figures

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/fig1-jk.pdf}

\clearpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/stan-across-strategy-variability2.pdf}

\clearpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{../figs/stan-gg-spoke2.pdf}

\label{fig:spokes}
\end{center}
\end{figure}

\clearpage

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../figs/stan-offset-break-anti-spaghetti-specializing.pdf}

\caption{Effect of specializing on year-to-year changes in revenue and revenue
variability for individual permit holders \emph{within} the `r nstr` most common
strategies. Changing species diversity from year-to-year is associated with
higher variability for individuals within the strategies above the zero line.
Specializing is associated with greater expected revenue ratios to the right of
the zero line and lower expected revenue ratios to the left of the zero line.
For example, individuals with setnet permits for salmon in Prince William Sound,
Cook Inlet, Kodiak, Bristol Bay, or the Alaska Peninsula (second purple dot from
right) target primarily sockeye salmon and experience a $\sim$1.5\% increase in
their year-to-year revenue ratio (horizontal axis) and a $\sim$0.5\% increase in
their revenue variability (vertical axis) for a 1\% decrease in their ratio of
year-to-year species diversity. These effects are estimated holding fishing
season length constant from year-to-year. Dots and line segments represent
medians and 50\% credible intervals of posteriors. The effect of generalizing
(increasing species diversity) is similar (Fig. S\ref{fig:mirror}).}

\clearpage

# Materials and methods

We obtained commercial fisheries landings and revenue data for all permit
holders in Alaska from `r range_yrs[1] - 1` to `r range_yrs[2]` from the Alaskan
Commercial Fisheries Entry Commission (CFEC). These data represent a total of
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD. We adjusted for
inflation by setting all revenues to 2009 USD [@bea2016]. We implemented
a number of filtering steps to focus on individuals actively engaged in
commercial fishing (Supporting Information). In particular, we removed permit
holders whose median revenue was less than \$10,000 USD to focus on individuals
for whom commercial fishing formed a substantial part of their income.

<!-- TODO Jordan: held by active fishers were not included in permit counts -->
<!-- / portfolios? Disregard this comment as you please but I thought I’d mention. -->

We used combinations of state and federal fishing permits held by an individual
in a specific year to define fishing "strategies", representing the species
targeted (Supporting Information). For example, we combined permits that were
otherwise the same except for vessel size (e.g. a longliner fishing sablefish
on a vessel under 60 ft was considered to have the same strategy as a longliner
fishing sablefish on a vessel over 60 ft), and we combined a number of permits
that were targeting a single species and differed only in region fished. For
example, someone fishing herring roe in Kodiak and someone fishing herring roe
in Alaska Peninsula were both considered to have a "herring roe" permit group.
For salmon permits, we formed salmon strategies based on similarities in gear
type and species composition (Supporting Information).

After this process of combining permits, we were left with `r n_grouped_permits`
unique fishing permit groups (Table S\ref{tab:strategies}), which we aggregated
within each person-year combination to form permit strategies. For example, if
someone fished halibut and sablefish in the same year, their strategy for that
year would be "halibut-sablefish". Specific details on our strategy definitions
are available in the Supporting Information.

Our models focused on species diversity as a possible predictor of revenue and
revenue variability while controlling for effort. For consistency with previous
analyses [@vedeld2007; @illukpitiya2008; @debela2012; @kasperski2013;
sethi2014], we calculated effective species diversity for permit holder $i$ and
time (year) $t$ as the inverse of Simpson's diversity index $\lambda$
[@simpson1949; @jost2006] (also referred to in economics as the
Herfindahl-Hirschman Index [@hirschman1964]) weighted by revenue $R$:

\begin{equation}
1/\lambda_{i,t} = 1 / \left(\sum\limits_{s=1}^{n_{i,t}}
  \left(R_{i,s,t}/ \sum\limits_{s=1}^{n_{i,t}} R_{i,s,t}\right)\right)^2,
\end{equation}

\noindent where $s$ indexes species from $1$ through $n$. We calculated effort
or effective season length as the sum of the season lengths for each permit
each year. Season length for a given permit was calculated as the number of
days between the first instance of fishing a permit and the last instance of
fishing a permit each year. For example, if someone fished for 30 days on a
salmon drift gillnet permit in Southeast Alaska and 40 days on a statewide
longline halibut permit, that individual's season length was calculated as 70
days.

## Hierarchical model

To jointly model revenue and revenue variability as a function of
individual-level covariates, we extended the basic variance-function regression
to a hierarchical Bayesian variance-function regression model with Gaussian
errors predicting $\log$ revenue, $\log(R_{i,t})$, for each fisher $i$ and time
$t$:

\begin{equation}
\log(R_{i,t}) \sim \mathrm{N} \left(\mu_{i,t}, \sigma_{i,t}^2 \right).
\end{equation}

\noindent Each year $t$ of revenue for fisher $i$ is assigned a strategy (permit
set) indexed by $j$ (Supporting Information, Table \ref{tab:strategies}) and
$\mu_{i,t}$ is modelled as:

\begin{equation}
\label{eq:mean}
\mu_{i,t} = \beta_{0,j,t} -
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} -
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1}),
\end{equation}

\noindent where $S_{i,t}$ is the log ratio of species diversity from
year-to-year, $\log \left(\mathrm{div}_{i,t}/\mathrm{div}_{i,t-1}\right)$,
$D_{i,t}$ is the log ratio of days fished from year-to-year, $\log
\left(\mathrm{days}_{i,t}/\mathrm{days}_{i,t-1}\right)$, and $I_{i,t}$ is an
indicator variable that takes a value $0$ if $\mathrm{div}_{i,t} \ge
\mathrm{div}_{i,t-1}$ (species diversity increasing; generalizing) and takes
a value $1$ if $\mathrm{div}_{i,t} < \mathrm{div}_{i,t-1}$ (species diversity
decreasing; specializing). Estimating a separate coefficient for the effect of
increasing diversity and decreasing diversity allows the costs and benefits of
these changes to be asymmetric (Fig. S\ref{fig:resid}).

We use $\log(R_{i,t-1}$) as an offset, and thus our model describes the log
ratio of revenue from year-to-year, i.e., $\log(R_{i,t}) - \log(R_{i,t-1})
= \log(R_{i,t}/R_{i,t-1})$. We model change in revenue because preliminary
analysis revealed non-stationary trends in revenue (resulting from experience or
other unmodelled factors). This approach eliminates having to deal with the
non-stationary time series and eliminates having to estimate thousands of
mean-revenue intercepts associated with individual fishers. We removed
person-year combinations without a subsequent year of revenue.

The $\beta$ terms represent estimated coefficients, some of which are allowed to
vary as "random effect" terms. The intercepts $\beta_{0,j,t}$ are allowed to
vary by strategy-year combinations, are centred on zero, and are constrained by
a normal distribution:

\begin{equation}
\beta_{0,j,t} \sim \mathrm{N} \left(0, \sigma^2_{\beta_{j,t}} \right).
\end{equation}

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.
The estimated $\beta_{j,t}$'s represent years when people with a particular set
of permits tended to collectively do better or worse than the long-term average
(Fig. S\ref{fig:str-yrs}). Therefore, an individual's expected change in revenue
(and variability) represents the expectation after accounting for the general
trend in revenue for that set of permits.

The slopes $\beta_{1,j}$ and $\beta_{1,j}$ are then allowed to vary by strategy
with estimated means:

\begin{align}
\beta_{1,j} &\sim \mathrm{N} \left(\mu_{\beta_1}, \tau^2_{\beta_1}\right),\\
\beta_{2,j} &\sim \mathrm{N} \left(\mu_{\beta_2}, \tau^2_{\beta_2}\right).
\end{align}

\noindent The $\beta_{1,j}$'s and $\beta_{2,j}$'s represent how much a 1\%
decrease and 1\% increase, respectively, in the ratio of species diversity from
year-to-year within a strategy translates to a given percent change in the ratio
of revenue from year-to-year. These are after controlling for changes in effort,
$\beta_3$, and the interaction between changes in effort and changes in species
diversity, $\beta_4$ and $\beta_5$.

Whereas traditional hierarchical linear models assume homoscedasticity --- that
the residual variance does not vary systematically --- our variance-function
regression model allows the residual variance to be heteroscedastic and vary as
a function of predictors. Instead of estimating a single residual error scale
term, $\sigma$, we model the scale of the residual error with another
hierarchical model with a similar form:

\begin{equation}
\label{eq:cv}
\sigma_{i,t} =
\exp \left( \gamma_{0,j} -
\gamma_{1,j} S_{i,t} I_{i,t} +
\gamma_{2,j} S_{i,t} I_{i,t} +
\gamma_3 D_{i,t} -
\gamma_4 S_{i,t} D_{i,t} I_{i,t} +
\gamma_5 S_{i,t} D_{i,t} I_{i,t}\right).
\end{equation}

\noindent Again, $S_{i,t}$ and $I_{i,t}$ represent, respectively, the log ratio
of species diversity from year-to-year and an indicator variable for increasing
or decreasing species diversity. We exponentiate the equation to ensure all
scale parameters, $\sigma_{i,t}$, are positive. Residuals from the mean
component of our model clearly show a "V"-shaped pattern, which the variance
component of our model can capture (Fig. S\ref{fig:resid}). Furthermore, the
downside residuals (year-individual data points with lower than expected
revenue) look qualitatively similar to the complete set of residuals (upside
and downside) (Fig. S\ref{fig:resid-downside}). Therefore, it seemed
appropriate to model the variability as a proxy for revenue risk.

The $\gamma$'s are estimated coefficients, three of which are allowed to vary by
strategy, constrained by normal distributions:

\begin{align}
\gamma_{0,j}  &\sim \mathrm{N} \left(\eta_0 + \eta_1 M_j + \eta_2 E_j, \tau^2_{\gamma_0}\right),\\
\gamma_{1,j}  &\sim \mathrm{N} \left(\mu_{\gamma_1}, \tau^2_{\gamma_1}\right),\\
\gamma_{2,j}  &\sim \mathrm{N} \left(\mu_{\gamma_2}, \tau^2_{\gamma_2}\right).
\end{align}

\noindent The $\gamma_{0,j}$ coefficients are modelled with two strategy-level
predictors. The symbols $M_j$ and $E_j$ represent the mean species diversity
and mean combined fishing season length (effort) for strategy $j$. The
coefficients $\eta_1$ and $\eta_2$ represent predictors in this strategy-level
regression estimating effects across strategies.

<!-- TODO: rerun with 2.14.1 -->

We fit our models with Stan 2.14.1 [@standevelopmentteam2016;
@standevelopmentteam2016a] and R 3.3.2 [@rcoreteam2016]. Stan implements the
No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm [@hoffman2014] to
perform Bayesian statistical inference. We assigned weakly informative priors
on all parameters: $N(0, 2^2)$ priors on all $\beta$, $\gamma$, and $\eta$
parameters, and half-$t(3, 0, 2)$ priors (i.e. degrees of freedom of 3 and
scale of 2) on all $\sigma$ and $\tau$. We ran four chains and 2,000 iterations
and discarded the first 1,000 iterations of each chain as warm up. We checked
for chain convergence visually with trace plots, ensured that $\hat{R}<1.05$
(the potential scale reduction factor) and that the effective sample size, as
calculated by the rstan R package [@standevelopmentteam2016], was greater than
200 for all parameters [@gelman2014]. We verified that our model returned
sensible estimates by comparing our estimates to an ad-hoc two-stage model fit
with the lme4 R package [@bates2015], where we first fit a mixed-effects
regression model to the mean, and then modelled the absolute residuals from
that first model in a second mixed-effects model representing the variance
component. We also validated the model with simulated data, and were able to
recover the true values (Supporting Information). Code used in our analysis is
available at <https://github.com/NCEAS/pfx-commercial/portfolios/>.

# Acknowledgments

TODO. National Center for Ecological Analysis and Synthesis (NCEAS) working
group *Applying portfolio effects to the Gulf of Alaska ecosystem: Did
multi-scale diversity buffer against the Exxon Valdez oil spill?*. Other
participants... Smith...

>>>>

@@

\dropcap{M}anaging natural resources and sustaining the livelihoods of those that depend
on their extraction is hard. These livelihoods tend to have high annual
variability in income relative to other professions [@mishra2002; @sethi2012b].
In addition to economic risk, such as changes in demand or prices, individuals
dependent on natural resources are also subject to biological and environmental
variability [@smith1986]. For example, drought and flooding are a major source
of risk for agricultural food security and farmers' incomes [@gregory2005], and
catastrophic disease outbreaks and wildfires increase risk for the logging
industry [@kirilenko2007].

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{../figs/fig1-jk.pdf}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{../figs/stan-across-strategy-variability2.pdf}

@@

Comparing single permit holders to individuals holding that same permit plus
additional permits illustrates the expected reduction in revenue variability
from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\figspokeall). For example, individuals fishing a halibut permit plus
one additional permit always had lower expected revenue variability compared to
individuals fishing only a halibut permit (median reduction of `r
100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually increased expected revenue, although the permits
themselves represent a significant expense.

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.8\textwidth]{../figs/stan-gg-spoke2.pdf}

\label{fig:spokes}
\end{center}
\end{figure*}

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given set of permits is more variable
(Fig. \ref{fig:within}). After accounting for fishing effort and changes in
annual average revenue for fishers with the same set of permits, specializing
tends to be associated with increased revenue but also increased variability
(Fig. \ref{fig:within}; Figs S\figfe, S\figre, S\ref{fig:noeffort}).
On average, there is a ~0.5% increase in the year-to-year revenue ratio per 1%
decrease in species diversity, and across strategies weighted equally, `r
g2_dens`% of the probability density supports a positive relationship between
specialization and revenue.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\textwidth]{../figs/stan-offset-break-anti-spaghetti-specializing.pdf}

\caption{Effect of specializing on year-to-year changes in revenue and revenue
variability for individual permit holders \emph{within} the `r nstr` most common
strategies. Changing species diversity from year-to-year is associated with
higher variability for individuals within the strategies above the zero line.
Specializing is associated with greater expected revenue ratios to the right of
the zero line and lower expected revenue ratios to the left of the zero line.
For example, individuals with setnet permits for salmon in Prince William Sound,
Cook Inlet, Kodiak, Bristol Bay, or the Alaska Peninsula (second purple dot from
right) target primarily sockeye salmon and experience a $\sim$1.5\% increase in
their year-to-year revenue ratio (horizontal axis) and a $\sim$0.5\% increase in
their revenue variability (vertical axis) for a 1\% decrease in their ratio of
year-to-year species diversity. These effects are estimated holding fishing
season length constant from year-to-year. Dots and line segments represent
medians and 50\% credible intervals of posteriors. The effect of generalizing
(increasing species diversity) is similar (Fig. S\figmirror).}

Changing (increasing or decreasing) an individual's fished species diversity
within the constraints of a set of permits tends to be associated with greater
expected variability or uncertainty in year-to-year revenue (Fig.
\ref{fig:within} strategies above zero; Figs. S\figfe, S\figre,
S\figmirror). This effect was strongest for individuals with a halibut
permit or halibut and sablefish permits. Individuals with these strategies
experienced a ~2% increase in variability for a 1% change in the year-to-year
ratio of species diversity (Fig. \ref{fig:within}). Becoming more generalized in
species diversity also leads to increased revenue variability (Fig.
S\ref{fig:mirror}A), suggesting that the act of changing strategies is
a contributor to increased variability of revenue.

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994, which potentially confounds our estimates with
a major regulatory change. Therefore, we refit our models allowing all
strategy-level effects involving halibut and sablefish permits to vary
separately before and after the introduction of IFQs. The introduction of IFQs
reduced variability in revenue by ~25% (TODO XX--XX 95% CI) for individuals with
only halibut or sablefish permits (Fig. S\figifq A). Furthermore, for most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\figifq B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\figifq B).

@@

There are many possible barriers to diversification for individuals relying on
natural resources for their livelihood. A primary barrier is the cost of
diversifying. For commercial fishers, purchasing additional licenses and gear
typically represents a substantial expense. Related barriers are apparent in
other natural resource sectors. For example, diversification has been positively
linked with total income or access to financial capital for farmers
[@abdulai2001; @barrett2001], small-scale fishing communities [@olale2012], and
those relying on forest resources [@illukpitiya2008]. Another major barrier to
diversification can be management restrictions. In commercial fisheries,
regulations that have been shown to reduce overfishing --- including improved
assessments [@melnychuk2017] and individual quota systems [@costello2008] ---
may ultimately restrict individual diversification [@smith1986; @kasperski2013]
or at least make developing a diverse fishing portfolio more expensive. However,
individual quota systems, in particular, may also reduce income variability
(Fig. S\figifq A) perhaps offsetting the effects of reduced diversification
[@holland2016].

@@

\acknow{TODO. National Center for Ecological Analysis and Synthesis (NCEAS) working
group *Applying portfolio effects to the Gulf of Alaska ecosystem: Did
multi-scale diversity buffer against the Exxon Valdez oil spill?*. Other
participants... Smith...
}
